Scientific Reasoning with LLMs

### 2024-10-29 docs/proposal/main.tex
Update main.tex

\paragraph{Dataset}
We plan to use the ScienceQA dataset \cite{lu2022learn}. ScienceQA is a multimodal dataset containing science questions and their answers.

>>>>

\paragraph{Dataset}
We plan to use the ScienceQA dataset \cite{lu2022learn}. The dataset includes a variety of science-related multimodal multiple-choice questions together with annotations of the answers that provide relevant lectures and explanations in Nature Science, Language Science and Social Science.
